### 2020-07-30 phase3/Project report/abstract.tex
update and organize files.

\begin{abstract}
 این بخش از یک پاراگراف تشکیل شده است که توضیحاتی کلی در مورد مساله و راه حل شما ارائه می‌دهد.
\end{abstract}