### 2020-07-30 phase3/Project report/main.tex

\documentclass{article}

\input{packages}
\title{گزارش پروژه پایانی }
\author{%
	مریم سادات هاشمی\\
	دانشکده مهندسی کامپیوتر\\
	دانشگاه علم و صنعت ایران\\
	\texttt{m\_hashemi94@comp.iust.ac.ir} \\
}

\begin{document}

\input{general}
\input{abstract}
\input{intro}
\input{literature}
\input{papers}
\input{implementation}
\input{ref}

\end{document}